Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-05-23 cordillera-cycle.tex
Develop results section.

All six simulations consistently produce two major glaciations during MIS~4 and
MIS~2 (Figs.~\ref{fig:timeseries} and~\ref{fig:snapshots}). However the timing
is much different. Notably the oceanic core forcing result in much too early
last glacial maximum. In general the Greenland-based simulation show much more
variability.

>>>>

Despite large differences in the input temperature offset time-series, the
model output presents consistent features that can be observed across the range
of forcing data used. In all simulations, ice cover is relatively restricted
during most of the glacial cycle, while two major glaciation events occur
during MIS~4 (61.9--55.4\,\unit{kyr}) and MIS~2 (29.5--16.9\,\unit{kyr},
Fig.~\ref{fig:timeseries}). A ice volume minimum is attained in between these
two events during MIS~3 (52.2--45.6\,\unit{kyr}).

On the other hand, the magitude and timing of these events vary significantly
between our simulations. For instance, GRIP and NGRIP forcing result in highest
variability in modelled ice volume, while simulations driven by oceanic records
and the NGRIP reach last glacial maximum ice volume prior to 20.0\,\unit{kyr}.

Snapshots of model output show relatively consistent patterns of glaciation
(Fig.~\ref{fig:snapshots}). In all simulations, a central ice cap persists over
the Skeena mountains between the two glaciation events. However, the size of
this ice cap, as well as the magnitude of the MIS~4, depends on the temperature
offset time-series used to drive the model.
